Generating Random Logic Programs Using Constraint Programming

### 2020-02-17 paper/paper.tex
Heavy editing

\usepackage[dvipsnames]{xcolor}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage[capitalise]{cleveref}
\usepackage{tikz}
\usepackage{mathrsfs}
\usepackage[nounderscore]{syntax}
\usepackage{blkarray}
\usepackage{siunitx}
\usepackage{amsthm}
\usepackage[round]{natbib}
\usepackage[inline]{enumitem}

@@

\renewcommand\fbox{\fcolorbox{red}{white}}
\newcommand{\hilight}[1]{\setlength{\fboxsep}{1pt}\colorbox{SpringGreen}{#1}}
\newcommand{\hlitem}{\stepcounter{enumi}\item[\hilight{\theenumi}]}

@@

\begin{document}
\bibliographystyle{plainnat}
\maketitle

\begin{abstract}
  We present a novel approach to generating random logic programs and
  random probabilistic logic programs using constraint programming. The
  generated programs are useful in empirical testing of inference algorithms,
  random data generation, and program learning. This approach has a major
  advantage in that one can easily add additional conditions for the generated
  programs. As an example of this, we introduce a new constraint for predicate
  independence with efficient propagation and entailment algorithms, allowing
  one to generate programs that have a certain independence structure. In order
  to generate valid probabilistic logic programs, we also present a new
  constraint for negative cycle detection. Finally, we provide a combinatorial
  argument for correctness and describe how the parameters of the model affect
  the empirical difficulty of the program generation task.
\end{abstract}

@@

How confidently can we claim that an algorithm works well if it is only tested
on a few types of problems? Perhaps the `inferior' algorithm is actually
better in some specific circumstances. Maybe there are identifiable
types of inputs that make every algorithm default to exponential behaviour
that could be easily overcome with the right strategy. At present, most
inference algorithms for probabilistic logic programs are only evaluated on at
most four different problems: sometimes just a single network
\citep{DBLP:journals/tplp/KimmigDRCR11,DBLP:journals/corr/abs-1112-3785},
sometimes two
\citep{DBLP:journals/corr/abs-1009-3798,DBLP:conf/ecai/BruynoogheMKGVJR10} or
four networks \citep{DBLP:conf/ijcai/VlasselaerBKMR15}, all coming from a range
of areas such as social networks and citation/genetic/biological data sets. To
better understand the strengths and weaknesses of these algorithms, along with
real data they should also be evaluated on a range of synthetic problems that
accurately represent the potential complexities that have to be handled by a
well-designed inference algorithm. Furthermore, random logic program generators
can be useful in combination with methods that generate random data with
probabilistic logic programs \citep{DBLP:conf/soict/Dries15} and can be used as
a component of learning.

Most current approaches to generating random logic programs are restrictive,
e.g., limited to clauses with only two literals
\citep{DBLP:conf/lpnmr/NamasivayamT09}, or to clauses of the form $a \gets \neg
b$ \citep{DBLP:journals/tocl/WenWSL16}, but others are more expressive, e.g.,
defining a program only by the (maximum) number of atoms in the body and the
total number of rules \citep{DBLP:conf/iclp/ZhaoL03}. We introduce a way to
generate random logic programs using a constraint model. The same model can
generate both probabilistic programs directly in the syntax of ProbLog
\citep{DBLP:conf/ijcai/RaedtKT07} as well as non-probabilistic Prolog programs.
For generated probabilistic programs to be valid, we use a custom constraint to
detect negative cycles (as described in \cref{sec:cycles}). A major advantage of
our constraint-based approach is that one can easily add additional constraints
to the model. To demonstrate that, in \cref{sec:independence} we present a
custom constraint with propagation and entailment algorithms that can ensure
predicate independence. \cref{sec:counting} also presents a combinatorial
argument for correctness, where we produce combinatorial expressions that count
the number of programs that the model should produce for various parameter
values. Finally, \cref{sec:experiments} shows how the model scales when tasked
with producing more complicated programs and identifies the relationships
between parameter values and the empirical hardness of the program generation
task.

Overall, our main contributions are concerned purely with logic programming-based
languages and frameworks, which capture a major fragment of statistical
relational learning \citep{DBLP:series/synthesis/2016Raedt}.
However, since probabilistic logic programming languages are closely related
to other areas of machine learning, including (imperative) probabilistic
programming \citep{DBLP:journals/ml/RaedtK15}, our results can lay the
foundations for exploring broader questions on generating and testing
programs/algorithms in machine learning.

@@

The basic primitives of logic programs are \emph{constants}, \emph{(logic)
  variables}, and \emph{predicates}. Each predicate has an \emph{arity} that
defines the number of terms that it can applied to. A \emph{term} is either a
variable or a constant, and an \emph{atom} is a predicate of arity $n$ applied
to $n$ terms. A \emph{formula} is a grammatically-valid expression that connects
atoms using conjunction ($\land$), disjunction ($\lor$), and negation ($\neg$).
A \emph{clause} is a pair of a \emph{head} (which is an atom) and a \emph{body}
(which is a formula). A \emph{(logic) program} is a multiset of clauses. Given a
program $\mathscr{P}$, a \emph{subprogram} $\mathscr{R}$ of $\mathscr{P}$ is a
subset of the clauses of $\mathscr{P}$ and is denoted by $\mathscr{R} \subseteq
\mathscr{P}$.

@@

\begin{constraint}
Let
  \[
    P = \{ h.\variable{predicate} \mid h \in \variable{heads} \}.
  \]
  Then
  \[
    \variable{nValues}(P) =
    \begin{cases}
      |\predicates{}| + 1 & \text{if } \variable{count}(\Box, P) > 0 \\
      |\predicates{}| & \text{otherwise.}
    \end{cases}
  \]
\end{constraint}

Here, $\variable{nValues}(P)$ counts the number of unique values in $P$.

@@

Given any clause, we can permute the variables in that clause without changing
the meaning of the clause or the entire program. Thus, we want to fix the order
of variables to eliminate unnecessary symmetries. Informally, we can say that
variable $X$ goes before variable $Y$ if the first occurrence of $X$ in either
the head or the body of the clause is before the first occurrence of $Y$. Note
that the constrains described in this section only make sense if $|\variables| >
1$. Also note that all definitions and constraints here are on a per-clause
basis.

@@

We add a number of redundant constraints to make search more efficient. First,
we can formally state that the positions occupied by different terms must be
different:

@@

In order to demonstrate the correctness of the model and explain it in more
detail, in this section we are going to derive combinatorial expressions for
counting the number of programs with up to $\maxNumClauses{}$ clauses and up to
$\maxNumNodes{}$ nodes per clause, and arbitrary $\predicates{}$,
$\arities{}$, $\variables{}$, and $\constants{}$\footnote{We checked that the
  our model agrees with the derived combinatorial formula in close to a thousand
  different scenarios. The details of this empirical investigation are omitted
  as they are not crucial to the thrust of this paper.}. To simplify the task,
we only consider clauses without probabilities and disable (negative) cycle
elimination. We also introduce the term \emph{total arity} of a body of a clause
to refer to the sum total of arities of all predicates in the body.

@@

\begin{definition}
  Let $\mathscr{P}$ be a probabilistic logic program. Its \emph{predicate
    dependency graph} is a directed graph $G_{\mathscr{P}} = (V, E)$ with the
  set of nodes $V$ consisting of all predicates in $\mathscr{P}$. For any two
  different predicates $\mathsf{P}$ and $\mathsf{Q}$, we add an edge from
  $\mathsf{P}$ to $\mathsf{Q}$ if there is a clause in $\mathscr{P}$ with
  $\mathsf{Q}$ as the head and $\mathsf{P}$ mentioned in the body. We say that
  the edge is \emph{negative} if there exists a clause with $\mathsf{Q}$ as the
  head and at least one instance of $\mathsf{P}$ at the body such that the path
  from the root to the $\mathsf{P}$ node in the tree representation of the
  clause passes through at least one negation node. Otherwise it is
  \emph{positive}. We say that $\mathscr{P}$ (or $G_{\mathscr{P}}$) has a
  \emph{negative cycle} if $G_{\mathscr{P}}$ has a cycle with at least one
  negative edge.
\end{definition}

@@

  We can now list the dependencies of each predicate:
  \begin{alignat*}{3}
    D_{\mathsf{parent}} &= \{ \mathsf{parent} \}, && D_{\mathsf{sibling}}
    &&= \{\mathsf{sibling}, \mathsf{parent} \},\\
    D_{\mathsf{mother}} &= \{ \mathsf{mother} \}, && D_{\mathsf{father}}
    &&= \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent} \}.
  \end{alignat*}
  Hence, we have two pairs of independent predicates, i.e., $\mathsf{mother}$ is
  independent from $\mathsf{parent}$ and $\mathsf{sibling}$.
\end{example}

@@

\begin{definition} \label{def:adjacency_matrix}
  An $|\predicates{}| \times |\predicates{}|$ adjacency matrix $\mathbf{A}$ with
  $\{ 0, 1 \}$ as its domain is defined by stating that $\mathbf{A}[i][j] = 0$
  if and only if, for all $k \in \{ 0, \dots, \maxNumClauses{} - 1 \}$, either
  \[
    \variable{heads}[k].\variable{predicate} \ne j
  \]
  or
  \[
    i \not\in \{a.\variable{name} \mid a \in
    \variable{bodies}[k].\variable{values} \}.
  \]
\end{definition}

@@

\section{NEGATIVE CYCLES} \label{sec:cycles}

Having no negative cycles in the predicate dependency graph is a requirement for
probabilistic logic programming language ProbLog \citep{kimmig2009trading},
although it has been shown how the requirement can be alleviated by introducing
negative probabilities \citep{DBLP:journals/ijar/BuchmanP17}. Ideally, we would
like to design a constraint for negative cycles similar to the constraint for
independence in the previous section. However, the difficulty with creating a
propagation algorithm for negative cycles is that there seems to be no good way
to extend \cref{def:adjacency_matrix} so that the adjacency matrix captures
positivity/negativity. Thus, we settle for an entailment algorithm with no
propagation.

@@

The vast majority (\SI{97.7}{\percent}) of runs finished in under
\SI{1}{\second}, while four instances timed out: all with $|\predicates| =
\maxNumClauses{} - |\predicates{}| = \maxNumNodes{} = 8$ and the remaining
parameters all different. This suggests that---regardless of parameter
values---most of the time a solution can be identified instantaneously while
occasionally a series of wrong decisions can lead the solver into a part of the
search space with no solutions.

@@

% TODO: Extra notes.
% 1. Randomness. The value heuristic is random because we want randomness. After
% finding one solution, one can continue the search for more, but they will be
% similar (acceptable if the search space is small and we want to find all
% solutions).
% 2. Logic programs don't have disjunctions and parentheses. Is there an easy
% way to eliminate them?
% 3. We can do the same thing for predicates within the body of a clause that we
% do with variables, i.e., predicates within a clause are permutable (except for
% the head predicate), so we can have a set of 'allowed' predicates.
% 4. One example of a clear bias exhibited by our model is that of complexity
% over simplicity, i.e., if a tree that represents the body of a clause can have
% up to $\maxNumNodes{}$ nodes---because the number of possible trees with $n$
% nodes grows with $n$---it is much more likely to have $\maxNumNodes{}$ or
% $\maxNumNodes{} - 1$ nodes than, e.g., one or two.

\section{CONCLUSIONS \& FUTURE WORK}

We were able to design an efficient model for generating both logic programs and
probabilistic logic programs. The model avoids unnecessary symmetries, generates
valid programs, and can ensure predicate independence. Note that our model
treats logically equivalent but syntactically different formulas as different.
While there are many situations where one would prefer to eliminate them like
symmetries, there are also situations where we do care about enumerating
different ways to express the same probability distribution or knowledge base.
For instance, one could look for the `best' logically equivalent formula, or
investigate whether some formulas result in faster inference than others.

Another topic worth mentioning is randomness. Most random models sample from a
well-defined probability distribution whereas a constraint model, while
sufficiently random, provides no such guarantees. In future work, it would be
interesting to examine the probability distribution of logic programs as
generated by our model, although it is not obvious how such a probability
distribution could be characterised.

>>>>

\usepackage[ruled,vlined]{algorithm2e}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage[capitalise]{cleveref}
\usepackage{tikz}
\usepackage{mathrsfs}
\usepackage[nounderscore]{syntax}
\usepackage{blkarray}
\usepackage{siunitx}
\usepackage{amsthm}
\usepackage[round]{natbib}
\usepackage[inline]{enumitem}

@@

\renewcommand\fbox{\fcolorbox{red}{white}}
\newcommand{\hilight}[1]{\setlength{\fboxsep}{1pt}\colorbox{lightgray}{#1}}
\newcommand{\hlitem}{\stepcounter{enumi}\item[\hilight{\theenumi}]}

@@

\begin{document}
\bibliographystyle{abbrvnat}
\maketitle

\begin{abstract}
  We present a novel approach to generating random logic programs and
  random probabilistic logic programs using constraint programming. The
  generated programs are useful in empirical testing of inference algorithms,
  random data generation, and program learning. This approach has a major
  advantage in that one can easily add additional conditions for the generated
  programs. As an example of this, we introduce a new constraint for predicate
  independence with efficient propagation and entailment algorithms, allowing
  one to generate programs that have a certain independence structure. To
  generate valid probabilistic logic programs, we also present a new constraint
  for negative cycle detection. Finally, we provide a combinatorial argument for
  correctness and describe how the parameters of the model affect the empirical
  difficulty of the program generation task.
\end{abstract}

@@

% Notes on papers that test ProbLog inference algorithms:
% - On the Implementation: published, one biological network
% -(removed) Nesting Probabilistic Inference: NOT published, one Alzheimer
% network
% -(removed) DNF Sampling: NOT published, two networks: a family tree and the
% Alzheimer network
% -ProbLog Technology: published, two networks: a custom theory with randomly
% generated data, and citation data
% -Anytime Inference: published, four networks: the Smokers social network,
% Alzheimer data, biological network of genetic data, data about the world wide
% web

%Interestingly, in the [???] of
%probabilistic logic programming, random logic program generators can be useful
%in combination with methods that generate random data with probabilistic logic
%programs \citep{DBLP:conf/soict/Dries15} and can be used as a component of
%learning.

Unifying logic and probability is a long-standing challenge in artificial
intelligence \citep{DBLP:journals/cacm/Russell15}, and, in that regard,
statistical relational learning (SRL) has developed into an exciting area that
mixes machine learning and symbolic (logical and relational) structures. In
particular, logic programs and probabilistic logic programs---including
languages such as PRISM \citep{DBLP:conf/ijcai/SatoK97}, ICL
\citep{DBLP:journals/ai/Poole97}, and ProbLog
\citep{DBLP:conf/ijcai/RaedtKT07}---are promising frameworks for codifying
complex SRL models. With the enhanced structure, however, inference becomes more
challenging as algorithms have to correctly handle hard and soft logical
constraints. At the moment, we have no precise way of evaluating and comparing
different inference algorithms. Incidentally, if one were to survey the
literature, one often finds that an inference algorithm is only tested on 1--4
data sets
\citep{DBLP:journals/tplp/KimmigDRCR11,DBLP:conf/ecai/BruynoogheMKGVJR10,DBLP:conf/ijcai/VlasselaerBKMR15},
originating from areas such as social networks, citation patterns, and
biological data. But how confidently can we claim that an algorithm works well
if it is only tested on a few types of problems?

About thirty years ago, SAT solving technology was dealing with a similar lack
of clarity \citep{DBLP:journals/ai/SelmanML96}. This changed with the study of
generation of random SAT instances against different input parameters (e.g.,
clause length and total number of variables) to better understand the behaviour
of algorithms and their ability to solve random synthetic problems.
Unfortunately, in the context of probabilistic logic programming, most current
approaches to random instance generation are very restrictive, e.g., limited to
clauses with only two literals \citep{DBLP:conf/lpnmr/NamasivayamT09}, or to
clauses of the form $a \gets \neg b$ \citep{DBLP:journals/tocl/WenWSL16},
although some are more expressive, e.g., defining a program only by the
(maximum) number of atoms in the body and the total number of rules
\citep{DBLP:conf/iclp/ZhaoL03}.

In this work, we introduce a constraint model for generating random logic
programs according to a number of user-specified parameters on the structure of
the program. In fact, the same model can generate both probabilistic programs
directly in the syntax of ProbLog \citep{DBLP:conf/ijcai/RaedtKT07} and
non-probabilistic Prolog programs. For generated probabilistic programs to be
valid, we use a custom constraint to detect negative cycles. A major advantage
of our constraint-based approach is that one can easily add additional
constraints to the model. To demonstrate that, we present a custom constraint
with propagation and entailment algorithms that can ensure predicate
independence. We also present a combinatorial argument for correctness, counting
the number of programs that the model produces for various parameter values.
Finally, we show how the model scales when tasked with producing more
complicated programs and identify the relationships between parameter values and
the empirical hardness of the program generation task.

Overall, our main contributions are concerned with logic programming-based
languages and frameworks, which capture a major fragment of SRL
\citep{DBLP:series/synthesis/2016Raedt}. However, since probabilistic logic
programming languages are closely related to other areas of machine learning,
including (imperative) probabilistic programming
\citep{DBLP:journals/ml/RaedtK15}, our results can lay the foundations for
exploring broader questions on generating models and testing algorithms in
machine learning.

@@

The basic primitives of logic programs are \emph{constants}, \emph{(logic)
  variables}, and \emph{predicates}. Each predicate has an \emph{arity} that
defines the number of terms that it can be applied to. A \emph{term} is either a
variable or a constant, and an \emph{atom} is a predicate of arity $n$ applied
to $n$ terms. A \emph{formula} is a grammatically-valid expression that connects
atoms using conjunction ($\land$), disjunction ($\lor$), and negation ($\neg$).
A \emph{clause} is a pair of a \emph{head} (which is an atom) and a \emph{body}
(which is a formula). A \emph{(logic) program} is a multiset of clauses. Given a
program $\mathscr{P}$, a \emph{subprogram} $\mathscr{R}$ of $\mathscr{P}$ is a
subset of the clauses of $\mathscr{P}$ and is denoted by $\mathscr{R} \subseteq
\mathscr{P}$.

@@

\begin{constraint}
Let
  \[
    P = \{ h.\variable{predicate} \mid h \in \variable{heads} \}.
  \]
  Then $\variable{nValues}(P) = |\predicates{}|$ if $\variable{count}(\Box, P) =
  0$ and $|\predicates{}| + 1$ otherwise, where $\variable{nValues}(P)$ counts
  the number of unique values in $P$.
\end{constraint}

@@

Given any clause, we can permute the variables in that clause without changing
the meaning of the clause or the entire program. Thus, we want to fix the order
of variables to eliminate unnecessary symmetries. Informally, we can say that
variable $X$ goes before variable $Y$ if the first occurrence of $X$ in either
the head or the body of the clause is before the first occurrence of $Y$. Note
that the constraints described in this section only make sense if $|\variables| >
1$. Also, note that all definitions and constraints here are on a per-clause
basis.

@@

We add a number of redundant constraints to make search more efficient. First,
we can state that the positions occupied by different terms must be different:

@@

To demonstrate the correctness of the model and explain it in more
detail, in this section we are going to derive combinatorial expressions for
counting the number of programs with up to $\maxNumClauses{}$ clauses and up to
$\maxNumNodes{}$ nodes per clause, and arbitrary $\predicates{}$,
$\arities{}$, $\variables{}$, and $\constants{}$\footnote{We checked that
  our model agrees with the derived combinatorial formula in close to a thousand
  different scenarios. The details of this empirical investigation are omitted
  as they are not crucial to the thrust of this paper.}. To simplify the task,
we only consider clauses without probabilities and disable (negative) cycle
elimination. We also introduce the term \emph{total arity} of a body of a clause
to refer to the sum total of arities of all predicates in the body.

@@

\begin{definition}
  Let $\mathscr{P}$ be a probabilistic logic program. Its \emph{predicate
    dependency graph} is a directed graph $G_{\mathscr{P}} = (V, E)$ with the
  set of nodes $V$ consisting of all predicates in $\mathscr{P}$. For any two
  different predicates $\mathsf{P}$ and $\mathsf{Q}$, we add an edge from
  $\mathsf{P}$ to $\mathsf{Q}$ if there is a clause in $\mathscr{P}$ with
  $\mathsf{Q}$ as the head and $\mathsf{P}$ mentioned in the body. We say that
  the edge is \emph{negative} if there exists a clause with $\mathsf{Q}$ as the
  head and at least one instance of $\mathsf{P}$ at the body such that the path
  from the root to the $\mathsf{P}$ node in the tree representation of the
  clause passes through at least one negation node. Otherwise, it is
  \emph{positive}. We say that $\mathscr{P}$ (or $G_{\mathscr{P}}$) has a
  \emph{negative cycle} if $G_{\mathscr{P}}$ has a cycle with at least one
  negative edge.
\end{definition}

@@

  We can now list the dependencies of each predicate:
  \begin{alignat*}{3}
    D_{\mathsf{parent}} &= \{ \mathsf{parent} \}, && D_{\mathsf{sibling}}
    &&= \{\mathsf{sibling}, \mathsf{parent} \},\\
    D_{\mathsf{mother}} &= \{ \mathsf{mother} \}, && D_{\mathsf{father}}
    &&= \{ \mathsf{father}, \mathsf{mother}, \mathsf{parent} \}.
  \end{alignat*}
  Hence, we have two pairs of independent predicates, i.e., $\mathsf{mother}$ is
  independent of $\mathsf{parent}$ and $\mathsf{sibling}$.
\end{example}

@@

\begin{definition} \label{def:adjacency_matrix}
  An $|\predicates{}| \times |\predicates{}|$ adjacency matrix $\mathbf{A}$ with
  $\{ 0, 1 \}$ as its domain is defined by stating that $\mathbf{A}[i][j] = 0$
  if and only if, for all $k \in \{ 0, \dots, \maxNumClauses{} - 1 \}$, either
  \[
    \variable{heads}[k].\variable{predicate} \ne j
  \]
  or $ i \not\in \{a.\variable{name} \mid a \in
  \variable{bodies}[k].\variable{values} \}$.
\end{definition}

@@

\section{NEGATIVE CYCLES} \label{sec:cycles}
% although some work has been done in overcoming this limitation
% \citep{DBLP:journals/ijar/BuchmanP17}

Having no negative cycles in the predicate dependency graph is a requirement of
ProbLog that makes the program well-defined \citep{kimmig2009trading}. Ideally,
we would like to design a constraint for negative cycles similar to the
constraint for independence in the previous section. However, the difficulty
with creating a propagation algorithm for negative cycles is that there seems to
be no good way to extend \cref{def:adjacency_matrix} so that the adjacency
matrix captures positivity/negativity. Thus, we settle for an entailment
algorithm with no propagation.

@@

The majority (\SI{97.7}{\percent}) of runs finished in under \SI{1}{\second},
while four instances timed out: all with $|\predicates| = \maxNumClauses{} -
|\predicates{}| = \maxNumNodes{} = 8$ and the remaining parameters all
different. This suggests that---regardless of parameter values---most of the
time a solution can be identified instantaneously while occasionally a series of
wrong decisions can lead the solver into a part of the search space with no
solutions.

@@

% TODO: Extra notes.
% 1. Randomness. The value heuristic is random because we want randomness. After
% finding one solution, one can continue the search for more, but they will be
% similar (acceptable if the search space is small and we want to find all
% solutions).
% 2. Logic programs don't have disjunctions and parentheses. Is there an easy
% way to eliminate them?
% 3. We can do the same thing for predicates within the body of a clause that we
% do with variables, i.e., predicates within a clause are permutable (except for
% the head predicate), so we can have a set of 'allowed' predicates.
% 4. One example of a clear bias exhibited by our model is that of complexity
% over simplicity, i.e., if a tree that represents the body of a clause can have
% up to $\maxNumNodes{}$ nodes---because the number of possible trees with $n$
% nodes grows with $n$---it is much more likely to have $\maxNumNodes{}$ or
% $\maxNumNodes{} - 1$ nodes than, e.g., one or two.
% 5. It can easily be shown that all generated logic programs are satisfiable
% 6. Logic programs typically only have a single conjunction with literals, but
% we can easily adapt the model to handle that.

\section{CONCLUSIONS}

We were able to design an efficient model for generating both logic programs and
probabilistic logic programs. The model avoids unnecessary symmetries, generates
valid programs, and can ensure predicate independence. Our constraint-driven
approach is advantageous in that one can easily add additional conditions on the
structure and properties of the program, although the main disadvantage is
that there are no guarantees about the underlying probability distribution from
which programs are sampled.

In addition, note that our model treats logically equivalent but syntactically
different formulas as different. This is so in part because designing a
constraint for logical equivalence fell outside the scope of this work and in
part because in some situations one might want to enumerate all ways to express
the same probability distribution or knowledge base, e.g., to investigate
whether inference algorithms are robust to changes in representation.
